A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-10 4_method.tex
rewrite method overview

\subsection{Method Overview}
\begin{enumerate}
\item Determine the beading strategy: the optimal number of beads and their widths in order to cover a given distance with those beads.
\item Compute the medial axis transform (MAT)
\item Discretize the MAT and add extra segments such that the gMAT divides a polygon in quads
\item Mark significant high curvature portions of the gMAT
\item Introduce bones on marked regions where we transition to a different number of beads
\item Add ticks on non-marked regions according to the beading strategy.
\item Connect ticks and transition nodes into toolpaths.
\end{enumerate}

>>>>

\subsection{Method Overview}
The global idea is that we locally decide on the number of beads everywhere in the input shape, then apply a beading strategy to determine the widths of the beads and then generate the toolpath locations and widths from this.
We decide on a bead count at locations which lie in the middle of the shape in some sense to be defined.
The beading strategy then gives us the beading widths and locations in between those center locations and the outline.
These beadings are then used to generate the toolpath junctions, which are connected together to form the extrusion toolpaths with varying width.

\begin{enumerate}
\item Compute a skeletonization of the outline shape based on the Voronoi diagram.
\item Use a significance measure to mark portions of the skeleton which lie in the center.
\item Determine the bead count values in the marked regions and handle transitions in bead count values.
\item Generate ticks along non-marked bones of the skeleton and connect the ticks together to extract the toolpaths.
\end{enumerate}
